---
title: " "
output:
  pdf_document:
    number_sections: TRUE
geometry: "left = 1in, right = 1in, top = 1in, bottom = 1in"
fontsize: 12pt
header-includes:
  - \usepackage{float}
  - \usepackage{sectsty}
  - \usepackage{paralist}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{dcolumn}
  - \usepackage{natbib}\bibliographystyle{agsm}
  - \usepackage[nottoc, numbib]{tocbibind}
bibliography: bibliography.bib
mainfont: Times New Roman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

\allsectionsfont{\centering}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{gobble}

\begin{centering}

\vspace{3cm}

\doublespacing
RESUMPTIVE RELATIVE CLAUSE DEPENDENCIES IN THE PROCESSING OF \\
FIRST AND SECOND LANGUAGE ENGLISH

\vspace{1.5cm}

\singlespacing
A DISSERTATION SUBMITTED TO THE GRADUATE DIVISION OF \\
THE UNIVERSITY OF HAWAI‘I AT MĀNOA IN PARTIAL FULFILLMENT OF \\
THE REQUIREMENTS FOR THE DEGREE OF

\vspace{1cm}

\doublespacing
DOCTOR OF PHILOSOPHY \\
IN \\
SECOND LANGUAGE STUDIES

\vspace{1.5cm}

\singlespacing
MAY 2023

\vspace{1.5cm}

\doublespacing
By \\
Fred Zenker

\vspace{1.5 cm}

\singlespacing
Dissertation Committee: \\
Bonnie D. Schwartz, Chairperson \\
Kamil Deen \\
Li 'Julie' Jiang \\
William O’Grady \\
Amy Schafer

\vspace{1.5 cm}

\flushleft
Keywords: resumption, resumptive pronoun, relative clauses, adult second language acquisition, adult second language processing

\end{centering}

\newpage

\pagenumbering{gobble}

\begin{centering}

{\bf Abstract}

\end{centering}

\spacing{1.5}

Insert abstract here.

\pagenumbering{roman}

\newpage

\centering
\raggedright
\newpage
\tableofcontents

\newpage

```{r acknowledgments, child='acknowledgments.Rmd'}
```

\newpage

```{r intro, child = 'introduction.Rmd'}
```
\pagenumbering{arabic}

\newpage

```{r methods, child = 'methods.Rmd'}
```

\newpage

```{r results, child = 'results.Rmd'}
```

\newpage

```{r discussion, child = 'discussion.Rmd'}
```

\newpage

```{r conclusion, child = 'conclusion.Rmd'}
```

\newpage

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage

```{r appendix, child = 'appendix.Rmd'}
```